An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-23 EconGrowth-R-Functions.Rnw
Now making a CI_delta vs. delta graph for CES in the presentation.

>>>>

<<CIvsParam_Graph, eval=TRUE>>=
#######################
# Creates a plot of confidence interval vs. value of a parameter with symbols being the 2-letter abbreviation
# for each country.
# model the model function you want to use. One of SF, CD, CDe, CES, or LINEX.
# param the parameter you want to plot. The options depend upon the model you want:
#       SF: lambda or m
#       CD: lambda, alpha, or beta
#      CDe: lambda, alpha, beta, or gamma
#      CES: gamma, lambda, delta_1, sigma_1, delta, or sigma
#    LINEX: a_0 or c_t
# energyType the energy type you want. One of Q, X, or U
# factor the factor you want to use in a single-factor model, if needed. One of K, L, Q, X, or U.
# textScaling the scale factor for labels on the graph
CIvsParamPlot <- function(model, param, energyType=NA, factor=NA, textScaling=1.0){
  # Get the data from the requested model
  if (model == "SF"){data <- singleFactorParamsDF(factor)} 
  else if (model == "CD"){data <- cobbDouglasParamsTableNoEnergyDF()}
  else if (model == "CDe"){data <- cobbDouglasParamsTableWithEnergyDF(energyType)}
  else if (model == "CES"){data <- cesParamsTableDF(energyType)}
  else if (model == "LINEX"){data <- linexParamsTableDF(energyType)}
  # Now get the data for the parameter requested
  if (param == "lambda"){
    x <- subset(data, select=lambda) # The column of lambdas
    xLabel <- "$\\lambda$"
    y <- subset(data, select=upperCI_lambda) - subset(data, select=lowerCI_lambda) # A column of CI values
  } else if (param == "m"){
    x <- subset(data, select=m) # The column of ms
    colnames(x) <- "m"
    if (factor == "K"){xLabel <- "$\\alpha$"}
    else if (factor == "L"){xLabel <- "$\\beta$"}
    else if ((factor == "Q") || (factor == "X") || (factor == "U")){xLabel <- "$\\gamma$"}
    y <- subset(data, select=upperCI_m) - subset(data, select=lowerCI_m) # A column of CI values
  } else if (param == "alpha"){
    x <- subset(data, select=alpha) # The column of alphas
    xLabel <- "$\\alpha$"
    y <- subset(data, select=upperCI_alpha) - subset(data, select=lowerCI_alpha) # A column of CI values
  } else if (param == "beta"){
    x <- subset(data, select=beta) # The column of betas
    xLabel <- "$\\beta$"
    y <- subset(data, select=upperCI_beta) - subset(data, select=lowerCI_beta) # A column of CI values
  } else if (param == "gamma"){
    x <- subset(data, select=gamma) # The column of gammas
    xLabel <- "$\\gamma$"
    y <- subset(data, select=upperCI_gamma) - subset(data, select=lowerCI_gamma) # A column of CI values
  } else if (param == "delta_1"){
    x <- subset(data, select=delta_1) # The column of delta_1
    xLabel <- "$\\delta_1$"
    y <- subset(data, select=upperCI_delta_1) - subset(data, select=lowerCI_delta_1) # A column of CI values
  } else if (param == "sigma_1"){
    x <- subset(data, select=sigma_1) # The column of sigma_1
    xLabel <- "$\\sigma_1$"
    y <- subset(data, select=upperCI_sigma_1) - subset(data, select=lowerCI_sigma_1) # A column of CI values
  } else if (param == "delta"){
    x <- subset(data, select=delta) # The column of delta
    xLabel <- "$\\delta$"
    y <- subset(data, select=upperCI_delta) - subset(data, select=lowerCI_delta) # A column of CI values
  } else if (param == "sigma"){
    x <- subset(data, select=sigma) # The column of sigma
    xLabel <- "$\\sigma$"
    y <- subset(data, select=upperCI_sigma) - subset(data, select=lowerCI_sigma) # A column of CI values
  } else if (param == "a_0"){
    x <- subset(data, select=a_0) # The column of a_0s
    xLabel <- "$a_0$"
    y <- subset(data, select=upperCI_a_0) - subset(data, select=lowerCI_a_0) # A column of CI values
  } else if (param == "c_t"){
    x <- subset(data, select=c_t) # The column of c_ts
    xLabel <- "$c_t$"
    y <- subset(data, select=upperCI_c_t) - subset(data, select=lowerCI_c_t) # A column of CI values
  colnames(y) <- "CI"
  yLabel <- paste("95\\% CI on", xLabel)
  data <- cbind(x, y)
  plot <- xyplot(data[ , 2] ~ data[ , 1], # data[ , 1] contains the the parameter; data[ , 2] contains the CIs
                 xlab=list(label=xLabel),
                 ylab=list(label=yLabel),
                             tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
                 panel = function(x, y){
                   ltext(x=x, y=y, labels=rownames(data))
                 })
  return(plot)
#CIvsParamPlot(model="SF", param="lambda", factor="Q")
#CIvsParamPlot(model="CD", param="alpha")
#CIvsParamPlot(model="CDe", param="gamma", energyType="Q")
#CIvsParamPlot(model="CES", param="delta", energyType="Q")
#CIvsParamPlot(model="LINEX", param="c_t", energyType="Q")

### 2013-03-23 EconGrowthSeminar.Rnw
Now making a CI_delta vs. delta graph for CES in the presentation.

\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
  Graph here of $CI_{\delta}$ vs. $\delta$ where each country abbreviation is plotted.
\end{frame}

>>>>

\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
<<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
CIvsParamPlot(model="CES", param="delta", energyType="Q")
@
\end{frame}
